\chapter*{Preface}
\begin{fullwidth}
\justify
\par This is a compilation for the pioneers into the stream of Robotics. Robotics is believed to have the potential to positively transform lives and work practices, raise efficiency and safety levels and provide enhanced levels of service. Even more, robotics is set to become the driving technology nurturing a whole new generation of autonomous devices and cognitive artefacts that, through their learning capabilities, interact seamlessly with the world around them, and hence, provide the missing link between the digital and physical world. The era has advanced so much that the neural networks escalate their accuracy to prove that they replicate human thought processes. There it becomes necessary for an engineer to engineer robots.
\vspace{5mm}
\paragraph{ } It is undeniable that a good technical book is a great source of knowledge and an effective tool to foster the real aspects of engineering into the students. Bearing this in mind, in order to make the first step of beginners a little more easy and grounded we bring this compilations of ours to light. For most of the novels into robotics, Arduino might be the entry point. This material focuses on Arduino right from its base, Programming Arduino with C, and interfacing ideas of several basic modules. Traversing through each and every journal and books that might equip us to get this done has really added up to our knowledge. We were able to correct many of our notions and make a journey through many concepts really worth understanding being technical aspirants. Taking another perspective we have recognised the importance of dedication, patience and commitment that we should cultivate to improve ourselves relentlessly.
\end{fullwidth}